---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r}
ggplot() +
  geom_line(aes(x = seq(-1,3,length.out = 187), y = test_set$Cooling.Load, color = 'True')) +
  geom_line(aes(x = seq(-1,3,length.out = 187), y = y_pred,color = 'Predicted'))+
  scale_color_manual(name=' ',values=c(True ='green', Predicted ='blue'))+
  ggtitle('Cooling.Load - True vs Predicted') +
  xlab(' ') +
  ylab('Cooling.Load')
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
